Foreign Exchange Speculation: An Event Study

### 2018-01-19 MDPI/MDPI_template/FinStudies.tex
Updated major reviewsions.

\begin{document}
\section{Introduction}
\added{Speculation can be stabilising or destabilising.} If speculation is based on information it is a stabilising force, providing liquidity and helping to ensure that markets swiftly find equilibrium. \citet{KeynesHedge} and \citet{HicksHedge} \deleted{for example} emphasise the role that speculation plays in facilitating financial market transactions \added{by providing liquidity that allows hedgers and other market participants to swiftly find counterparties with the need for large prices concessions.}. Speculators offer a service for a fee that is determined by the return on their activity.  \replaced{While speculators may be trading on information or noise, informed speculators will tend to drive out the uninformed noise-traders according to \citet{FriedmanPositive}.}{\citet{FriedmanPositive} argued that even where there are a mixture of infomed and unnformed speculators, the informed woudl tend to buy when prices were below intrinsic value and sell when above, making profits, stabilising the market and driving the loss-making uninformed speculators out of teh market.} \deleted{However, the later} \citet[p. 101]{Keynes1936} \added{also had a later, more negative view of speculation.  Here he} regarded speculation as a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd'\added{. Uninformed speculators may dominate} and \citet{Delong1990noise} provides a model of cases where speculative noise provides a constraint on informed traders benefiting from their knowledge. Now speculation is an uninformed and destabilising force.  \added{We have therefore two concepts of speculation: one that is random and disruptive and one that is informed and beneicial in its provison of liqidity.

The debate about the relative merit of these two concepts of speculation continues to the current era where there has been much discussion over the role that speculation played in the boom and bust of commodities prices in the period between 2006 and 2007.  A common story that has encouraged congressional investigation says that wild speculation drove oil and other commodities prices well above their fundamental value causing harship for commodity consumers and a subsequent collapse that was equally disruptive for the producders.  \citet{PindyckSpec} show a broad movement of commodities prices not linked to fundaments that they argue is caused by speculation.  \citet{TangSpec} suggest that this speculative disruption was exacerbated by speculation on commodity indices.  However, \citet{ScottSpec} do not find a link between speculative positions and excess price movements in commodities.   \citet{Jacksspec} documents the history of attacks on speculation following price volatility.}

This paper evaluates the relative importance of these two concepts of speculation by investigating the relationship between the intensity of speculation and the weight of speculative positions relative to subsequent movement of foreign exchange prices.\footnote{\label{FX}The foreign exchange market is chosen for this study because it is the largest and most liquid financial market in the world.  The latest survey taken by the Bank for International Settlements (BIS) in April 2016 estimated average daily turnover at \$5.1trn with average daily spot transactions of \$1.7trn See \citet{BISFX2016}.  The cost of trading in this market, when measured in terms of the size of the bid-ask spread, is extremely low. An analysis by \citet{Steely2013} of the bid-ask spreads for USD-JPY, GBP-USD and EUR-USD for the period January 2001 to 2005 finds that the average spread for each is 0.342\%, 0.305\% and 0.326\% respectively.  This would be the cost for a round-trip (buying and selling immediately).}  \added{The intenisty of speculation is measured with the use of option risk-reversal skew.  As these become more extreme it signals that expectations of buyers and sellers in the foreign exchange options market have diverged significantly from the forward rate.  Weight of speculative positions is measured by the net long or short of speculative accounts in the futures market. If the movement of prices towards equilibrium, \emph{price discovery} is facilitated by order flow from informed traders (as has been asserted theoetically by \citet{Glosten1985Bid} and \citet{Kyle1985Continuous} while being demonstrted empirically by \citet{Lyons1995Microstructure} and \citet{Evans2002Order} and \citet{rime2010exchange}, speculative sentiment and positions would be part of the price discovery process if informed and would disript this process if not. Therefore,}if speculators are informed their activity drives exchange rates towards equilibrium and prices should follow a random walk after these extremes \added{of speculative sentiment or position}; if speculators are uninformed and their activity can be regarded as noise, the most extreme speculative sentiment and the time when speculators have the greatest weight in the market should correspond with the greatest deviation of prices from fundamental value, when reversals are most likely to take place.

@@

The comparison of informed and uninformed traders is a central component of microstructure research.  At the heart of the \citet{Kyle1985Continuous} model of market-making is the interaction of orders from the informed and the uninformed.  On the assumption that uniformed orders arrive in a random fashion, the weight of orders reveals the direction of private information and should encourage adjustment of the bid-ask spread as part of the process of price discovery.  \citet{glosten1985bid} presents a model where the bid-ask spread is a function of adverse selection, being caused by the risk that orders come from informed traders.

@@

\replaced{More recently the debate has move towards the way that noise-trading speculators may affect welfare and how that could be contained. \citet{Tobin1982} and \citet{Tobvin} developed the argument for the eponymous transaction tax that would seek to limit the influence of exchange rate speculation.  \citet{ERW} use a series of fundamentals to show how speculation casued unwarranted devaluations during the period of the European Exchange Rate Mechanism (ERM).   \citet{Tobin3} use this experience to re-state the call for a tax to reduce speculation.  However, if speculation is informed and part of the process of price discovery this tax can be counterproductive as it will reduce liquidity and may cause evengreater volatility. This is a point made by \citet{Mayer} and \citet{McKinnon}.

The call for a tax on speculative activity in financial markets arose again in the middle of the first decade of the new century as a result of surge in commodities prices that was experienced in the period 2005 to 2007. Focused mostly on oil but encompassing many other energy, metal and food commodities, one argument attributed the rise in prices again to speculative actvity.  See..}.

\section{Measuring speculation}
\added{It is common practice to back market expectations out of information drawn from option prices.}  \footnote{If the risk-reversal for a 1-month USD/CAD is quoted at 0.15-0.28\% and the implied volatility is 8.50\%, the market-maker would be willing to buy the 1-month 25 delta USD-put-CAD-call at 8.65\% and sell the USD-call-CAD-put at 8.50\%.  The dealer pays 0.15\%.  Alternatively, the dealer would sell a 25 delta call at 8.78\% and buy the USD-call-CAD-put at 8.50\%, earning 0.28\%. See \citet{Global} for a technical review. }  Therefore, the relationship between implied volatility for calls and implied volatilities for puts for the same delta and maturity strike is an indication of how much more expensive calls are relative to the equivalent put or as the market bias towards puts over calls and as an indication of market sentiment or related market positioning.  The larger the absolute level of the risk-reversal skew, the greater the relative price and, if the deviation is based on information, subsequent price action should be zero on average; if the deviation is based on noise, this movement should be reversed.  See \citet{Yan2011} and \citet{FengZhangFriesen} for some analysis of implied volatility in the equity market.

>>>>

\begin{document}
\section{Introduction}
\added{Speculation can be stabilising or destabilising.} If speculation is based on information it is a stabilising force, providing liquidity and helping to ensure that markets swiftly find equilibrium. \citet{KeynesHedge} and \citet{HicksHedge} \deleted{for example} emphasise the role that speculation plays in facilitating financial market transactions \added{by providing liquidity that allows hedgers and other market participants to swiftly find counterparties without the need for large prices concessions. In this version, speculators} \deleted{Speculators} offer a service for a fee that is determined by the return on their activity.  \replaced{\citet{FriedmanPositive} argued that even where there is a mixture of infomed and unnformed speculators, the informed woudl tend to buy when prices were below intrinsic value and sell when above, making profits, stabilising the market and driving the loss-making uninformed speculators out of business.}{While speculators may be trading on information or noise, informed speculators will tend to drive out the uninformed noise-traders according to \citet{FriedmanPositive}.} \deleted{However, the later} \citet[p. 101]{Keynes1936} \added{also had a later, more negative view of speculation.  Here he} regarded it as a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd''\added{. Uninformed speculators may now dominate} and \citet{Delong1990noise} provide a model \deleted{of cases} where speculative noise \replaced{constrains}{provides a constraint on} informed traders \added{from} benefiting from their knowledge. Now speculation is an uninformed and destabilising force.  \added{We have therefore two concepts of speculation: one that is random and disruptive and one that is informed and beneicial in its provison of liqidity.

The debate about the relative merit of these two concepts of speculation continues. There has been particular focus on commodities markets and foreign exchange markets.  \citet{Jacksspec} documents a long history of attacks on speculation following price volatility.} This has been particularly evident in commodities and foreign exchange markets.  There has been much discussion over the role that speculation played in the boom and bust of commodities prices in the period between 2006 and 2007.  \citet{TangSpec} suggest that this disruption was exacerbated by newly estabilished commodity indices that encoraged speculation.

There have also been investigations of the link between speclulation or noise trading and price misalignments or volatility across a range of other asset marketsA.  \citet{Verma} examine the link between noise trading and equity markets; \citet{Hongjun} asks whether speculation in aggregate is just random noise lacking influence on prices.  Howevever, foreign exchange has been a particular focus as a consequence of its liquidity, volatility and the way that speculative attacks appear to have infringed on government soverignty.  See \citet{Dornbusch1988} in geneal and \citet{Eichengreen1988} for discussion of the speculative attacks on the European exchange rate system.  \citet{Eichengreen1994} use a set of fundamentals to show that speculative attacks drove exchange rates away from their fundamental value. However, others have made the case that speculative is a key part of the forign exchange market, providing liquidity and contribuing to stability.  See \citet{Mayer1985} and \citet{McKinnon1986}.

There is no consensus and the the debate enters policy circles with the suggestion that a tax on financial transactions could reduce speculation and thereby limit misalignment and volatility. \citet[pp.158]{TobinTax} and \citet{Tobin1988a} say that such a tax would "throw some sand in the well-greased wheels." of the foreign exchange market. At face value the tax has the advantage of improving market efficiency and raising funds for other welfare-enhancing acitvity.  However, this is only the case if speculation is uninformed and destabilising.  If it is informed and contributes to stability the tax will come at a cost.

This paper evaluates the relative importance of these two concepts of speculation by investigating the relationship between the intensity of speculation and the weight of speculative positions relative to subsequent movement of foreign exchange prices. \added{The foreign exchange market is appropriate this study because it is central to the call for the introduction of a transaction tax as a consequence of it being the largest and most liquid financial market in the world.  The latest survey taken by the Bank for International Settlements (BIS) in April 2016 estimated average daily turnover at \$5.1trn with average daily spot transactions of \$1.7trn See \citet{BISFX2016}.  The cost of trading in this market, when measured in terms of the size of the bid-ask spread, is extremely low. An analysis by \citet{Steely2013} of the bid-ask spreads for USD-JPY, GBP-USD and EUR-USD for the period January 2001 to 2005 finds that the average spread for each is 0.342\%, 0.305\% and 0.326\% respectively.  This would be the cost for a round-trip (buying and selling immediately).This makes it relatively attractive for speculators.

The intenisty of speculation is measured in two ways: speculative sentiment and speculative positions.  Speculative sentiment is identified with the use of option risk-reversal skew.  As these become more extreme it signals that expectations of future value in the foreign exchange options market have diverged significantly from the appropraite forward rate.  The Weight of speculative positions is identified with US regulatory data of the psotions held by type of participant in the futures market.  Net long and net short are open positions held by spculators relative to overall activit in the market. See Section \ref{secref:measure} for full data details.}

@@

@@

\added{This study is about short-term movements in foreign exchange prices.  The event windows are between 1 week and 4 weeks in length. While the interpretation of economic fundamentals can drive prices, market posotions and liquidity trades will also be important.  Even at longer horizons it is often very difficult to connect exchange rate movements to specific events. \citet{Meese1983Empirical} find that forecasts using exchange rate models cannot beat a random walk while \citet{ChinnModel} updated the study to find very similar results. 
.  
The foreign exchange market is primarily a dealer-orientated market.  It is largely consistent with the theortical microstructure models that have been presented by the likes of \citet{Kyle1985Continuous} and \citet{glosten1985bid}. The interaction of informed and uninformed traders drives the price-discovery process: if the uninformed traders are random, the market-maker earns the bid-ask spread; if informed traders arrive they drive the price towards equilibrium.}

If the movement of the price of foreign exchange towards equilibrium, \emph{price discovery} is facilitated by order flow from informed traders (as has been asserted theoetically by \citet{Glosten1985Bid} and \citet{Kyle1985Continuous} while being demonstrted empirically by \citet{Lyons1995Microstructure} and \citet{Evans2002Order} and \citet{rime2010exchange}, speculative sentiment and positions would be part of the price discovery process if informed and would disript this process if not. Therefore,}if speculators are informed their activity drives exchange rates towards equilibrium and prices should follow a random walk after these extremes of speculative sentiment or position; if speculators are uninformed and their activity can be regarded as noise, the most extreme speculative sentiment and the time when speculators have the greatest weight in the market should correspond with the greatest deviation of prices from fundamental value, when subsequent price reversals are most likely to take place.

\section{Measuring speculation}\label{secref:measure}
\added{There are two steps: identify speculation and assess what happens when it becomes extreme.  If speculation is uninformed, extremes should cause a divergence from fundamental value and a price reversal should be anticipated; if informed and part of the price-discovery process, extreme speculation achieves a new equilibrium and the following price performance should be a random walk.

The measurement of speculative intensity must identify how far speculators believe that the market will move in a particular direction. In the absence of a daily survey of speculators, this study uses a unique series of option\emph{risk-reversal skew} as an measure of speculative sentiment.  The risk-reversal data is very difficult to obtain in an over-the-counter market like foreign exchange where there is no centralised exchange to record and collect information, generally being the property of quoting institutions.  The risk-reversals are the average prices quoted at 10:00 GMT by major banks on the Thomson-Reuters composite option pages (OPT1)  for the period between January 2 1996 and September 6 2002.  The risk-reversals are the spread of implied volatility for a 1 month 25 delta at-the-money call option relative to the equivalent put.  Risk-reversal skew is the relative price of currency put and call options for the same strike price.} The risk-reversal skew is the relationship between a call option and the equivalent put. Equivalence here being measured by the delta or relationship between movement of the underlying price and the movement of the option price.  While the \citet{Black1973Options} model is the basis for valuing options where the price of a non-dividend paying stock trades at a discount to the forward rate equal to the risk free rate, the forward rate in a currency option is determined by the relative interest rate differential between the two currencies.   The \citet{GarmanKohlhagan} adjustment that accounts for the difference in interest payments on the two currencies is used.   The spot discount is determined therefore by the relative interest rate differential for the appropriate maturity.  1 month in this case.  This model allows the market practice of pricing options from the volatility implied by the model.  In other words, the Garman-Kohlhagan is used to extract the volatility that is implied by a specific foreign exchange option price given the strike and other parameters.

It is common practice to back market expectations out of information drawn from option prices.  See \citet{Malickoption} and \citet{Pochin} for the general approach that combines the implied volatility, risk-reversal and strangles to infer a mixed distrubtion that can be inferreed as the risk-neutral probabiolity density function for a particular asset. See \citet{Gaati} an application on the Yen-dollar exchange rate where expectations are affected by central bank intervention. Using the risk-reversal is a simplified version of that where the skew is used to infer positive and expectations relative to the appropriate forward rate.  See ??? for previous uses of this data.}

If the risk-reversal for a 1-month USD/CAD is quoted at 0.15-0.28\% and the implied volatility is 8.50\%, the market-maker would be willing to buy the 1-month 25 delta USD-put-CAD-call at 8.65\% and sell the USD-call-CAD-put at 8.50\%.  The dealer pays 0.15\%.  Alternatively, the dealer would sell a 25 delta call at 8.78\% and buy the USD-call-CAD-put at 8.50\%, earning 0.28\%. See \citet{Global} for a technical review.  Therefore, the relationship between implied volatility for calls and implied volatilities for puts for the same delta and maturity strike is an indication of how much more expensive calls are relative to the equivalent put or as the market bias towards puts over calls and as an indication of market sentiment or related market positioning.  The larger the absolute level of the risk-reversal skew, the greater the relative price and, if the deviation is based on information, subsequent price action should be zero on average; if the deviation is based on noise, this movement should be reversed.  See \citet{Yan2011} and \citet{FengZhangFriesen} for some analysis of implied volatility in the equity market.
